---
title: "Live Session Unit 04 Assignment"
author: "Audrene Tiakor"
date: "February 5, 2019"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

#Question 1: Harry Potter Cast (50%)

##a. Website URL
*http://www.imbdb.com/title/tt1201607/fullcredits?ref_=tt_ql_l.

##b. Scrape page with R package and make it a data frame

### First load the necessary packages to scrape the webpage:
```{r libraries}
library(XML)
library(dplyr)
library(tidyr)
library(stringi)
library(rvest)
library(ggplot2)
library(RCurl)

```
### Taking the table of the Cast in order of crediting and puting it in a data frame:

```{r scrapping}
harryp<-read_html("https://www.imdb.com/title/tt1201607/fullcredits?ref_=tt_ql_l")
harryp_table<-html_nodes(harryp, "table")
harryp_cast<-html_table(harryp_table)
harryp_cast2<-data.frame(harryp_cast[3])

```
##c. Clean up the table:
### Delete the first row in data frame b/c it is blank:

```{r delete_1st_row, echo=TRUE}
harryp_cast2 <- harryp_cast2[-1, ]
```
### Delete columns 'X1' and 'X3' because we don't need those:
```{r trash_columns, echo=TRUE}
names(harryp_cast2)
harryp_cast3<-harryp_cast2[,c(2,4)]

```
### Rename 'X2' and 'X4' to 'Actor' and 'Character':

```{r rename, echo=TRUE}
names(harryp_cast3) <- c("Actor", "Character")
```
### Split 'Actor' column into 'Firstname' and 'Surname':
```{r split, echo=TRUE}
harryp_cast4 <- harryp_cast3 %>% separate(col = Actor, into = c("FirstName", "Surname"), sep = " (?=[^ ]+$)")

```
### Delete row with observation 'Rest of cast listed alphabetically':
```{r delete, echo=TRUE}
harryp_cast4 <- harryp_cast4[-92, ]

```
### Replace Mr. Warwick two characters with a neater listed name:
```{r name_replace, echo=TRUE}
harryp_cast4[10,3]<-'Griphook/Professor Filious Flitwick'

```

##e. Present the first 10 rows of the data frame:
```{r frame, echo=TRUE}
head(harryp_cast4,10)

```
#Question 2: SportsBall (50%)

##a. Website URL
*http://www.espn.com/nba/team/stats/_/name/sa/san-antonio-spurs.

##b. Scrape page with R package and make it a data frame
### First load the necessary packages to scrape the webpage:
```{r libraries_again}
library(XML)
library(dplyr)
library(tidyr)
library(stringi)
library(rvest)
library(ggplot2)
library(RCurl)

```

```{r scrapping_2}
stars<-read_html("http://www.espn.com/nba/team/stats/_/name/sa/san-antonio-spurs")
stars_table<-html_nodes(stars, "table")
stars_df<-html_table(stars_table, fill = TRUE)
stars_names<-data.frame(stars_df[2])
stars_stats<-data.frame(stars_df[8])
name_stats<-cbind(stars_names, stars_stats)

```
##c. Clean up the table:
### Split column name into two columns: "Name" and "Position":
```{r split_2}
shooting.stats <- name_stats %>% separate(col = "Name", into = c("Player", "Position"), sep = " (?=[^ ]+$)")
head(shooting.stats)
```
### Delete the totals row in the table:
```{r delete_2}
shooting.stats <- shooting.stats[-c(16),]

```
##d. Create colorful bar chart that shows 'Field Goals Percentage Per Game' for each player
```{r colorful_plot}
pl <- ggplot(shooting.stats, aes(x=Player,y=`FG.`,color=Position, fill=Position)) + geom_bar(stat="identity") +
  ggtitle("Field Goal % per Game by Player (San Antonio Spurs)") + xlab("Player Name") + ylab("Field Goal % per Game") +
  coord_flip() 
print (pl)

```
