---
title: "Live Session Unit 01 Assignment"
author: "Audrene Tiakor"
date: "February 15, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
*This assignment is to familarize onesself with R as a calculator.

#Question 1: Basic Math (20 pts)

###a. The log of a positive number
```{r log}
log(4)
```
###b. What is the default base for the log function? Calculate the log of your previous number with a different base.
```{r log_diff_base}
log(4, base=4)
```
###c. The log of a negative number. (explain the answer)
```{r log_neg}
log(-3)
```
* An error message was returned because the log function is only defined for positive inputs. (x>=0)

###d. The squareroot of a positive number.
```{r sqrt}
sqrt(7)
```

#Question 2: Random Number Generation (15 pts)

###a. Create a vector of 15 standard normal random variables. Calculate its mean and SD:
```{r random}
x <-rnorm(15, 0, 1)
x
mean(x)
sd(x)
```

###b. Change the mean to 10 and the SD to 2. Recalculate the vector of 15 random variables. Find the mean and SD.
```{r random2}
x <-rnorm(15, 10, 2)
x
mean(x)
sd(x)
```

###c. Why are the means and SD not exactly the same as the means and SD's specified in the function?
*Since the vector we created 'x' is of random variables, as the variables change, so does the mean and sd. 

#Question 3: Vector Operations (40 pts)
###a. Create a vector of weights for 6 individuals in kg which are 60, 72, 57, 90, 95, 72
```{r weight}
w<-c(60, 72, 57, 90, 95, 72)
w
```
###b. Create a vector of heights for the 6 individuals in m which are 1.80, 1.85, 1.72, 1.90, 1.74, 1.91
```{r height}
h<-c(60, 72, 57, 90, 95, 72)
h

```
###c. create a data frame using the vectors w and h
```{r df}
people<-data.frame(w,h)
people

```
###d. Create a scatterplot of weight vs. height. Interpret the scatterplot.
```{r scat}
 
 plot(w, h, main = "Weight vs Height Correlation", xlab = "Weight (kg)", ylab = "Height (m)", frame = TRUE)
abline(lm(h ~ w, data = people), col="blue")

```
###e. Calculate the BMI for each individual. (BMI= weight in kg divided by the square of the height in m)
```{r bmi}
 
 options(scipen = 999, digits = 4)
 bmi <-function(w,h){
 w/(h^2)
   }
people$bmi = bmi(people$w,people$h) 
print(people$bmi)

```
###f. Calculate the mean for weight
```{r mean}
 people$mean_of_weight = mean(w)
 people
 people$diff =(people$w)
 print(people)
```
###g. Subtract the mean from each value of weight
```{r sub}
  sd_top<- function(w){
    mean(w) - w

 }
people$diff = sd_top(people$w)
print(people)

```
###f. Sum the result
```{r sum}
  sum(people$diff)

```

# Question 4: My Data Science Profile
```{r profile}
setwd("C:\\Users\\Audrene\\Desktop\\Doing Data Science\\HW_1")
Audrene <- read.table(file = "profile.csv",header = T,sep = ",")
Audrene
barplot(Audrene$Ranking,names.arg=Audrene$Categories,xlab="Skills",ylab="Ranking",col="blue", main="Data Science Profile",border="red")

```
