---
title: "Live Session Unit_3 Assignment"
author: "Audrene Tiakor"
date: "January 27, 2019"
output: 
html_document:
  keep.html=True
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Question 1: GitHub Cloning (On to Local Machine)
### Steps:

1. Type the following url into browser:
2. https://github.com/caesar0301/awesome-public-datasets
3. Under the repository name, click clone or download.
4. In the clone, in the HTTPS section, copy the clone URL for the repository.
   Open Git Bash.
5. Change the current working directory to the location where you want the cloned    directory to be (i.e.)
6. Type command 'git clone', then past the URL from step 2. It should look like     this: $ git clone https://github.com/awesomedata/awesome-public-datasets.git
   Now you should have a cloned copy of the files in the place where you set your    current working directory.

#Question 2: Data Summary
### a.
#### Read in the csv file 'titanic.csv, assign it to 'df'

```{r read_table, include=TRUE}
setwd("C:\\Users\\Audrene\\Desktop\\SMU_MSDS_PROGRAM\\Term1_spring2019\\MSDS6306\\HW\\Live_session_3\\awesome-public-datasets\\Datasets") 
df <- read.table(file = "titanic.csv", header = T, sep = ",")
```

###b.
#### Output total number of females and males with a frequency plot

```{r sumary, include=TRUE}
summary(df$Sex)
table(df$Sex)
barplot(table(df$Sex), main= "Sex of Passengers On the Titanic", xlab = "Sex", ylab = "Frequency")

```

###c.
#### Application of the 'apply' function for multiple columns

```{r apply, include=TRUE}
sapply(df[,c("Age","Fare", "Survived")],mean, na.rm = TRUE)

```

#Question 3: Function Building

*First need to read in the data set sleep_data_01.csv (found at http://talklab.psy.gla.ac.uk/L1_labs/lab_1/homework/index.html)

```{r sleep, include=TRUE}
setwd("C:\\Users\\Audrene\\Desktop\\SMU_MSDS_PROGRAM\\Term1_spring2019\\MSDS6306\\HW\\Live Session Unit 3 Assignment")
sleep <-read.csv(file = "sleep_data_01.csv", header = T, sep = ",")
```
*We need to create a function(x), that when out data sleep is read into it, will return MedianAge, SelfEsteem, SE_SD, and DurationRange. Here are the steps:

1. Create objects for the following: median Age, minimum and maximum duration of sleep, mean and standard deviation of RSES:

2. Create 'data.frame' Object Called 'report':

3. Change Column Names of 'report':

4. Round Numerical Outputs in 'report' to 2 digits

##FINAL RESULT
```{r funtion(x), include=TRUE}
sleep.function <- function(x) {
  
  med.age.sleep = median(x$Age,na.rm=TRUE)
  max.sleep.duration = max(x$Duration, na.rm=TRUE)
  min.sleep.duration = min(x$Duration, na.rm=TRUE)
  DurationRange = max.sleep.duration - min.sleep.duration 
  mean.RSES.sleep = mean(x$RSES, na.rm=TRUE)
  sd.RSES.sleep = sd(x$RSES, na.rm = TRUE)
  report <- data.frame(med.age.sleep, mean.div.5= mean.RSES.sleep/5, sd.div.5 = sd.RSES.sleep/5, sleep.range = max.sleep.duration - min.sleep.duration)
  names(report)[1] <- paste("MedianAge")
  names(report)[2] <- paste("SelfEsteem")
  names(report)[3] <- paste("SE_SD")
  names(report)[4] <- paste("DurationRange")
  report = round(report, digits =2)
  return(report)
  
}
sleep.function(sleep)
```
#Question 4: FiveThirtyEight Data

###a. Install the fivethirtyeight package:
```{r install, include=TRUE}
library(fivethirtyeight)
```

###b. Assign 2nd Data Set to 'df':
*Note: "college_recent_grads" is the 22nd data set in package fivethirtyeight
```{r df, include=TRUE}
data("college_recent_grads")
df<- college_recent_grads

```
###c. Write Out URL in a Comment
* Use the following code to find the URL:
```{r vignette, include=TRUE}
vignette("fivethirtyeight", package = "fivethirtyeight")
```
* https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/


###d. Dimensions and Column Names for 'df':
```{r col_dim, include=TRUE}
dim(df)
names(df)

```
#Question 5: Data Summary
###a. Number of Columns and Column Names for 'df':

```{r names, ECHO=TRUE}
colnames(df)
ncol(df)
```

###b. Major Count
*Want to generate a count of each major category in the data frame 'df':
```{r count, ECHO=TRUE}
library(plyr)
 major_count<- count(df, "major_category")
```

###c. Barplot of 'major_count'
*We want to label the x and y axis, label the title with something informative, and flip the barplot horizontally:
```{r barplot, ECHO=TRUE}
library(ggplot2)
 ggplot(data=major_count, aes(x = major_category, y=freq))+geom_bar(stat="identity", color = "blue", fill="blue")+coord_flip()+ggtitle("Frequency of Major Categories")
```
###d. Write the fivethirtyeight data to a csv file, without row labels:

save<-write.csv(df, file = "fivethiertyeight.csv",row.names=FALSE, na="")




# GitHub Link 
https://github.com/atiakor0/SMU_MSDS_6306.git


