---
title: "LSA_11"
author: "Audrene Tiakor"
date: "March 28, 2019"
output: html_document
---

---

```{r,lib}
library(dplyr)
library(tidyr)
library(plyr)
library(jsonlite)
library(caret)
```
1-3. Use the most updated code that is zipped with this. It fixes the grep problem by pasting a string with bracketed regular expression. Use the "snippet" instead of the headline. Look at the data from 1989 to 1999.
```{r, code}
# First, need to put specialized API key
NYTIMES_KEY = "R4womc6lruskQnucRE9npn1QbyGrtTqF" #Your Key Here … get from NTY API website

# Let's set some parameters
term <- "central+park+jogger" # Need to use + to string together separate words
begin_date <- "19890101"
end_date <- "19991231"

baseurl <- paste0("http://api.nytimes.com/svc/search/v2/articlesearch.json?q=",term,
                  "&begin_date=",begin_date,"&end_date=",end_date,
                  "&facet_filter=true&api-key=",NYTIMES_KEY, sep="")

initialQuery <- jsonlite::fromJSON(baseurl)
maxPages <- round((initialQuery$response$meta$hits[1] / 10)-1)

pages <- list()
for(i in 0:maxPages){
  nytSearch <- jsonlite::fromJSON(paste0(baseurl, "&page=", i), flatten = TRUE) %>% data.frame() 
  message("Retrieving page ", i)
  pages[[i+1]] <- nytSearch 
  Sys.sleep(10) 
}

#gather the pages into one dataframe
allNYTSearch <- rbind_pages(pages)
#see if it is populated
dim(allNYTSearch)
head(allNYTSearch, 5)
```


4. To provide external cross validation (50%/50%). Create a training and test set from the total number of articles. Train the classifier on the training set and create your confusion matrix from the test set. Make sure and provide the confusion matrix.
```{r,cross}
#cross validation: training/test set (50%/%50, training/test respectively)
allNYTSearch$NewsOrOther = ifelse(allNYTSearch$response.docs.type_of_material == "News","News","Other")
seed= 123
train_perc = .5
train_indices = sample(seq(1,length(allNYTSearch),by = 1), train_perc*length(allNYTSearch))
TrainingNYT = allNYTSearch[train_indices,]
TestNYT = allNYTSearch[-train_indices,]
```


#Classification Using Snippet

```{r,news}

#This function returns P(News | Keyword) 
#P(News|KW) = P(KW|News)* P(News) / P(KW)

Pnews_word = function(key_word = "jogging", TrainingNYT)
{
  print(key_word)
  NewsGroup = TrainingNYT[TrainingNYT$NewsOrOther == "News",]
  OtherGroup = TrainingNYT[TrainingNYT$NewsOrOther == "Other",]
  
  pNews = dim(NewsGroup)[1] / (dim(NewsGroup)[1] + dim(OtherGroup)[1])
  pOther = 1 - pNews
  
  pKWGivenNews = length(grep(paste("\\b",key_word,"\\b",sep=""),NewsGroup$response.docs.snippet,ignore.case = TRUE))/dim(NewsGroup)[1]
  pKWGivenOther = length(grep(paste("\\b",key_word,"\\b",sep=""),OtherGroup$response.docs.snippet,ignore.case = TRUE))/dim(OtherGroup)[1]
  
  pKW = length(grep(paste("\\b",key_word,"\\b",sep=""),TrainingNYT$response.docs.snippet,ignore.case = TRUE))/dim(TrainingNYT)[1]
  
  pNewsGivenKW = pKWGivenNews*pNews/pKW
  pOtherGivenKW = pKWGivenOther*pOther/pKW
  
  return(pNewsGivenKW)
}


theScoreHolderNews = c()
theScoreHolderOther = c()
articleScoreNews = 0;
articleScoreOther = 0;


for (i in 1 : dim(TestNYT)[1])  #This loop iterates over the articles
{
  
  articleScoreNews = 0; 
  articleScoreOther = 0;
  theText = unlist(strsplit(gsub("[^[:alnum:] ]", "", TestNYT$response.docs.snippet[i]), " +"))
  for(j in 1 : length(theText))  #This loop iterates over the headline (each word)
  {
    articleScoreNews = articleScoreNews + Pnews_word(theText[j],TestNYT)
    articleScoreOther = articleScoreOther + (1 - Pnews_word(theText[j],TestNYT))
  }
  theScoreHolderNews[i] = articleScoreNews
  theScoreHolderOther[i] = articleScoreOther
}


# Classify the aricle as News or Other based on a given piece of information from the article.
TestNYT$Classified = ifelse(theScoreHolderNews > theScoreHolderOther,"News","Other")
```
5a. Confusion Matrix for Snippet
```{r,mat}
#Confusion Matrix
result_snippet<-table(TestNYT$NewsOrOther,TestNYT$Classified)
confusionMatrix(result_snippet)
```

#Classification Using Headline

```{r,head}
#This function returns P(News | Keyword) 
#P(News|KW) = P(KW|News)* P(News) / P(KW)
Pnews_word = function(key_word = "jogging", TrainingNYT)
{
  print(key_word)
  NewsGroup = TrainingNYT[TrainingNYT$NewsOrOther == "News",]
  OtherGroup = TrainingNYT[TrainingNYT$NewsOrOther == "Other",]
  
  pNews = dim(NewsGroup)[1] / (dim(NewsGroup)[1] + dim(OtherGroup)[1])
  pOther = 1 - pNews
  
  pKWGivenNews = length(grep(paste("\\b",key_word,"\\b",sep=""),NewsGroup$response.docs.headline.main,ignore.case = TRUE))/dim(NewsGroup)[1]
  pKWGivenOther = length(grep(paste("\\b",key_word,"\\b",sep=""),OtherGroup$response.docs.headline.main,ignore.case = TRUE))/dim(OtherGroup)[1]
  
  pKW = length(grep(paste("\\b",key_word,"\\b",sep=""),TrainingNYT$response.docs.headline.main,ignore.case = TRUE))/dim(TrainingNYT)[1]
  
  pNewsGivenKW = pKWGivenNews*pNews/pKW
  pOtherGivenKW = pKWGivenOther*pOther/pKW
  
  return(pNewsGivenKW)
}

theScoreHolderNews = c()
theScoreHolderOther = c()
articleScoreNews = 0;
articleScoreOther = 0;


for (i in 1 : dim(TestNYT)[1])  #This loop iterates over the articles
{
  
  articleScoreNews = 0; 
  articleScoreOther = 0;
  
  theText = unlist(strsplit(gsub("[^[:alnum:] ]", "", TestNYT$response.docs.headline.main[i]), " +"
                            ))
  for(j in 1 : length(theText))  #This loop iterates over the headline (each word)
  {
    articleScoreNews = articleScoreNews + Pnews_word(theText[j],TestNYT)
    articleScoreOther = articleScoreOther + (1 - Pnews_word(theText[j],TestNYT))
  }
  theScoreHolderNews[i] = articleScoreNews
  theScoreHolderOther[i] = articleScoreOther
}

# Classify the aricle as News or Other based on a given piece of information from the article.
TestNYT$Classified = ifelse(theScoreHolderNews > theScoreHolderOther,"News","Other")
```
5a. Confusion Matrix for Headline
```{r,sn}
#Confusion Matrix
result_headline<-table(TestNYT$NewsOrOther,TestNYT$Classified)
confusionMatrix(result_headline)
```
7. Use your statistics from the last two questions to assess whether the headline or the snippet makes for a better classifier.

The snippet makes for a better classifier than the headline. Assessing the accuracy of both matricies, the accuracy of the snippet is better than the headline.

