---
title: "Live_Session_Unit_5"
author: "Audrene Tiakor"
date: "February 11, 2019"
output: 
html_document:
  keep.html=True
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
*First start with importing the following libraries:

```{r libraries}
library(rvest)
library(tidyr)
library(dplyr)
library(ggplot2)
```
## Question 1: Data Munging (30 pts):
###a. Import 'yob2016.txt' in R, Give columns names (Name, Gender, Count), name resulting data frame 'df'


```{r import}
setwd("C:\\Users\\Audrene\\Desktop\\SMU_MSDS_PROGRAM\\Term1_spring2019\\MSDS6306\\HW\\Live_session_5")

```
```{r yob}
yob <- readLines("yob2016.txt")
df<-data.frame(yob, stringsAsFactors=FALSE)
df<-df %>% separate(yob,c("Name","Gender","Count"))
df$Count<-as.numeric(df$Count)
```
###b. Display the summary and structure of df
```{r display}
str(df)
summary(df)
```
###c. Find which name is spelled with 'yyy' and display it
```{r which}
grep("yyy$",df$Name,value = TRUE)
df[which(df$Name == "Fionayyy"), ]
```
###d. Remove the name spelled with 'yyy' and save the object as y2016
```{r delete}
y2016<-df[-212,]
```

##Question 2: Data Merging (30 pts)
###a. Import 'yob2015.txt' in R, Give columns names (Name, Gender, Count), name resulting data frame 'y2015'
```{r y2015}
yob2 <- readLines("yob2015.txt")
y2015<-data.frame(yob2, stringsAsFactors=FALSE)
y2015<-y2015 %>% separate(yob2,c("Name","Gender","Count"))
y2015$Count<-as.numeric(y2015$Count)
```
###b. Display the last 10 rows in the dataframe. Describe something you find interesting
```{r tail}
tail(y2015,10)
```
*Comment: What's interesting about the last 10 rows in the dataframe is that they are all males, not females are in the last 10 of the y2015 dataframe. 

###c. Merge y2016 and y2015 by your 'Name' and 'Count'Column, name it 'final'
```{r merge}
final <- merge(y2015,y2016,by= c('Name', 'Gender'))
final[is.na(final), ] 
```
*I merged it by name and gender to clean up the fact that I had two gender columns, gender.x and gender.y. Since we are merging both data sets, I figured it would be cleaner and also better to merge the genders especially for 3c. I left the count.x and count.y columns alone because in number 3 we actually end up making a 'total' column, which requires we sum the count.x and count.y columns.

##Question 3: Data Summary (30 points):
###a. Create a new column called 'Total' that adds the count of 2016 and 2015 together
```{r total}
final$Total<-final$Count.x + final$Count.y
head(final)
sum(final$Total)
```
###b. Sort the data by 'Total'. Give top 10 most popular Names.
```{r sort}
final<-final[order(-final$Total),]
head(final,10)
```
* The top 10 most popular popular names are: Emma, Olivia, Noah, Liam, Sophia, Ava, Mason, William, Jacob, and Isabella.

###c. Client is expecting a girl. Omit the boys and give top 10 most popular girl's names
```{r sort_girls}
top_10<-head(final[final$Gender == 'F', ],10)
```
###d. Write top 10 girl names to a CSV file. Leave out other columns entirely.
```{r write_csv}
write.csv(top_10, file = "top_10_girl_names.csv",row.names=FALSE)
```

##Question 4: Upload to GitHub (10 pts):

*URL to my Github: https://github.com/atiakor0/SMU_MSDS_6306.git

*Instructions on how to access hw on Github:

1. click on the folder titled 'MSDS_6306_HW'
2. click on the folder titled 'live_session_5'
3. in this folder you will find the following files:

+ Readme file, with what is contained in the live_session_5 folder
+ Rmarkdown file, with matching HTML file
+ Codebook
+ raw data sets 'yob2016.txt' and 'yob2015.txt'
+ finalized data set for client named 'top_10_girl_names.csv'

